Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-10 tex/VHzQ.tex
tex/mn2e removed
tex update

We have compiled a list of 463 quasars with redshifts $z\geq5.00$. We
use all the $z\geq5.00$ quasars that have been discovered,
spectroscopically confirmed and published as of 2018 December 31 (MJD
58483). We then obtain optical, near-infrared and mid-infrared
photometry for the spectral dataset. The near-infrared data comes from
two sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT,
primarily, but not exclusively, as part of the UKIRT Infrared Deep Sky
Survey \citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the
VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}. The
mid-infrared, $\lambda=3-30\mu$m wavelength data is from the the
Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010,
Cutri2013} mission. For reference, Figure~\ref{fig:filters} displays
the wavelength and normalised transmission of the filters in question.

@@

We use data from the the beginning of the WISE mission \citep[2010 January; ][]{Wright2010} through the fifth-year of NEOWISE-R operations \citep[2018 December;]{Mainzer2011}.  There are several  major \href{https://irsa.ipac.caltech.edu/Missions/wise.html}{data releases} and catalogues based on the WISE mission. Here we use two: the WISE \href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE Data release} and the recently released ``unWISE Catalog'' \citet{Schlafly2019}. The AllWISE program combines the W1 and W2 Single-exposure data from all WISE survey phases (4-Band Cryo, 3-Band Cryo and Post-Cryo; 2010-01-07 thru 2011-02-01) survey phases, and the W3 and W4 from the 4-Band Cryo phase. The unWISE effort\footnote{\href{http://unwise.me}{http://unwise.me}} is the unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.

@@

\subsection*{Author Contributions}   
N.P.R. initiated the project, compiled the list of $z>5.00$ quasars, wrote most of the analysis code, developed the the plotting scripts, and developed and wrote the initial and subsequent drafts of the manuscript.
%%
N.J.G.C. supplied the critical near-infrared expertise and database for which the bulk of the project relies. N.J.G.C. also contributed directly to the writing of the manuscript.

@@

%\bibliographystyle{apj}
\bibliographystyle{mn2e}
\bibliography{tester_mnras}

>>>>

We have compiled a list of 463 quasars with redshifts $z\geq5.00$. We
use all the $z\geq5.00$ quasars that have been discovered,
spectroscopically confirmed and published as of 2018 December 31 (MJD
58483). We then obtain optical, near-infrared and mid-infrared
photometry for the spectral dataset. The near-infrared data comes from
two sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT,
primarily, but not exclusively, as part of the UKIRT Infrared Deep Sky
Survey \citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the
VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}. The
mid-infrared, $\lambda=3-30\mu$m wavelength data is from the 
Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010,
Cutri2013} mission. For reference, Figure~\ref{fig:filters} displays
the wavelength and normalised transmission of the filters in question.

@@

We use data from the beginning of the WISE mission \citep[2010 January; ][]{Wright2010} through the fifth-year of NEOWISE-R operations \citep[2018 December;]{Mainzer2011}.  There are several  major \href{https://irsa.ipac.caltech.edu/Missions/wise.html}{data releases} and catalogues based on the WISE mission. Here we use two: the WISE \href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE Data release} and the recently released ``unWISE Catalog'' \citet{Schlafly2019}. The AllWISE program combines the W1 and W2 Single-exposure data from all WISE survey phases (4-Band Cryo, 3-Band Cryo and Post-Cryo; 2010-01-07 thru 2011-02-01) survey phases, and the W3 and W4 from the 4-Band Cryo phase. The unWISE effort\footnote{\href{http://unwise.me}{http://unwise.me}} is the unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.

@@

\subsection*{Author Contributions}   
N.P.R. initiated the project, compiled the list of $z>5.00$ quasars, wrote most of the analysis code, developed the plotting scripts, and developed and wrote the initial and subsequent drafts of the manuscript.

N.J.G.C. supplied the critical near-infrared expertise and database for which the bulk of the project relies. N.J.G.C. also contributed directly to the writing of the manuscript.

@@

%\bibliographystyle{apj}
%\bibliographystyle{mn2e}
\bibliographystyle{mnras}
\bibliography{tester_mnras}
